flowCore: data structures package for flow cytometry data

### 2008-07-10 inst/doc/HowTo-flowCore.Rnw
moved all plotting stuff to flowViz, flowCore now issues a message to attach flowViz for all plotting
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@31029 bc3139a8-67e5-0310-9ffc-ced21a209358
fixed inconsitencies in the splitting methods
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@32646 bc3139a8-67e5-0310-9ffc-ced21a209358

Much of the more sophisticated visualization of \Rclass{flowFrame} and
\Rclass{flowSet} objects, including an interface to the
\Rpackage{lattice} graphics system is implemented by the
\Rpackage{flowViz} package, also included as part of
Bioconductor. However, \Rpackage{flowCore} does implement some basic
plotting facilities using the standard \Rfunction{plot} function. The
basic plot provides a simple pairs plot of all parameters:

<<Plot1, fig=true, echo=true>>=
plot(x)
@

@@

<<FilterSet1, echo=true, results=verbatim>>=
fset1 = filterSet(
	rectangleGate(filterId="Fluorescence Region","FL1-H"=c(50,100),"FL2-H"=c(50,100)),
	norm2Filter(filterId="Morphology Gate","FSC-H","SSC-H",scale=2),
	~ `Fluorescence Region` & `Morphology Gate`,
	~ `Fluorescence Region` | `Morphology Gate`,
	Debris ~ ! `Morphology Gate`,
	~ `Fluorescence Region` %&% `Morphology Gate`
)
fset1

>>>>

Much of the more sophisticated visualization of \Rclass{flowFrame} and
\Rclass{flowSet} objects, including an interface to the
\Rpackage{lattice} graphics system is implemented by the
\Rpackage{flowViz} package, also included as part of
Bioconductor. Here, we will only introduce the standard
\Rfunction{plot} function. The basic plot provides a simple pairs plot
of all parameters:

<<Plot1, fig=true, echo=true>>=
library(flowViz)
plot(x)
@

@@

<<FilterSet1, echo=true, results=verbatim>>=
fset1 = filterSet(
	rectangleGate(filterId="Fluorescence Region","FL1-H"=c(50,100),
                      "FL2-H"=c(50,100)),
	norm2Filter(filterId="Morphology Gate","FSC-H","SSC-H",scale=2),
	~ `Fluorescence Region` & `Morphology Gate`,
	~ `Fluorescence Region` | `Morphology Gate`,
	Debris ~ ! `Morphology Gate`,
	~ `Fluorescence Region` %&% `Morphology Gate`
)
fset1
